method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added ANOVA for Levator

@@

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

@@

@@

>>>>

data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
data_ER$block[data_ER$trigger == 21] <- "1_view_neu"

@@

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Levator activity")

@@

# Bayes Factors
EMGLevReg_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                      data = EMG_reg,
                                      progress = FALSE)

EMGLevReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf)

EMGLevReg_con <- cbind(EMGLevReg_con,
                       format(effectsize::t_to_eta2(t = EMGLevReg_con$t.ratio,
                                                    df_error = EMGLevReg_con$df,
                                                    ci = 0.95),digits = 2))

colnames(EMGLevReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

EMGLevReg_con[1,1] <- "$View_{negative} - Distraction$"
EMGLevReg_con[2,1] <- "$View_{negative} - Distancing$"
EMGLevReg_con[3,1] <- "$View_{negative} - Suppression$"
EMGLevReg_con[4,1] <- "$Distraction - Distancing$"
EMGLevReg_con[5,1] <- "$Distraction - Suppression$"
EMGLevReg_con[6,1] <- "$Distancing - Suppression$"

@@

# figure
FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Levator activity")
